---
title: "p8105_hw1_yh683"
author: "Yining He"
date: "2024-09-15"
output: github_document
---

Before the Problem I have install.packages("palmerpenguins")in the conclose directly.

# Problem 1

```{r, echo=FALSE}
library(tidyverse)
library(palmerpenguins)
data("penguins", package = "palmerpenguins")

summary(penguins)
```

## 1.Short description of the penguins dataset

### Important variables 

**(1)Species:Adelie(152), Chinstrap(68), Gentoo(124)**

**(2)island:Biscoe(168), Dream(124), Torgersen(52)**

**(3)bill_length_mm:The length of the penguin's bill in millimeters.**

**(4)bill_depth_mm:The depth of the penguin's bill in millimeters.**

**(5)flipper_length_mm:The length of the penguin's flipper in millimeters.**

**(6)body_mass_g:The body mass of the penguin in grams.**

**(7)sex： Female(165), Male(168)**

**(8)year:The year in which the penguin was observed(2007-2009)**

### The size of the dataset

```{r, echo=TRUE}
# rows of dataset
nrow(penguins)
# columns of dataset
ncol(penguins)
```
**The rows of this dataset is 344 and the columns of this dataset is 8.**


### The mean of  flipper length
```{r, echo=FALSE}
mean(pull(penguins, flipper_length_mm), na.rm = TRUE)
```
**The mean of flipper_length is 200.9152 mm.**

## 2.Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x)

input data and pakages
```{r, echo=FALSE}
# Load necessary libraries
library(ggplot2)
library(palmerpenguins)

# Load the penguins dataset
data("penguins", package = "palmerpenguins")

```
Create the scatterplot
```{r yx_scatter}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + 
  geom_point() +
  labs(title = "Scatterplot of Flipper Length vs Bill Length",
       x = "Bill Length (mm)",
       y = "Flipper Length (mm)",
       color = "Species") +
  theme_minimal()

```
Export the first ggplot.
```{r, echo=FALSE}
ggsave("scatter_plot.png")
```

# Problem 2

## Create the Data Frame

```{r echo=FALSE}
library(tidyverse)
example_df = tibble(
  vec_char = c("A","B","C","D","E","F","G","H","I","J"),
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric > 0,
  vec_factor = factor(c("LEVEL1","LEVEL2","LEVEL3",
                        "LEVEL1","LEVEL2","LEVEL3",
                        "LEVEL1","LEVEL2","LEVEL3",
                        "LEVEL1"))
)
example_df

```
## Taking the Mean of Each Variable

mean_sample <- mean(df %>% pull(sample_data))  
mean_logical <- mean(df %>% pull(logical_vector))  
mean_character <- mean(df %>% pull(character_vector))  
mean_factor <- mean(df %>% pull(factor_vector))

**sample_data**: This works because it is numeric. mean() can compute the mean of numeric vectors.

**logical_vector**: This works because logical values in R are coerced to numeric when using mean(), where TRUE becomes 1 and FALSE becomes 0.

**character_vector**: This fails because characters cannot be coerced to numeric directly. mean() doesn't know how to handle non-numeric values.

**factor_vector**: This fails because factors are internally stored as integers, but mean() does not automatically convert these integers in a meaningful way.

## Applying as.numeric() to Each Variable

```{r, warning=FALSE, results='hide'}
print(as.numeric(example_df[["vec_char"]]))
print(as.numeric(example_df[["vec_logical"]]))
print(as.numeric(example_df[["vec_factor"]]))

```
The outputs occur because as.numeric() shows differently for each variable type: it returns NA for character vectors since they can't be directly converted to numbers; it converts logical vectors to 0 (for FALSE) and 1 (for TRUE); and it converts factor vectors to their internal numeric codes representing the factor levels (e.g., "Level1" = 1, "Level2" = 2).










